Bounds on the dimension of consistent convex surrogates

### 2020-05-26 neurips-20/cvx-flats.tex
Another pass over finite case proofs.

\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, define $\gamma'$ to be $\gamma$ restricted to the simplex $\Delta_{\supp(p)}$.
	Consider the ambient space of both $\S_{\gamma_r}(p)$ and $\S_{\gamma'_r}(p)$ to be $\reals^\Y$.
	Then $\S_{\gamma_r}(p) = \S_{\gamma'_r}(p)$.
\end{lemma}
\begin{proof}
	We trivially have $\S_{\gamma_r}(p) \supseteq \S_{\gamma'_r}(p)$ since the latter is simply a projection down to an affine subspace of the former.

	Now to see $\S_{\gamma_r}(p) \subseteq \S_{\gamma'_r}(p)$, take some $v \not \in \S_{\gamma'_r}(p)$.
	Then for all $\epsilon > 0$, we have either $p \pm \epsilon v \not \in \gamma'_r$.
	Moreover, this must be because $p \pm \epsilon v$ leaves the simplex $\Delta_{\supp(p)}$, as we have $p$ on the relative interior of that such simplex.
	While $p \pm \epsilon v$ may be in $\simplex$, we must then have $p \mp \epsilon v$ outside the simplex.
	As $\gamma_r \subseteq \simplex$, we have $v \not \in \S_{\gamma_r}(p)$.

	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
%	\begin{align*}
%	\dim(\S'_{\gamma_r}(p)) &= \dim(\S_{\gamma_r}(p)) + \dim(P) - \dim(\S_{\gamma_r}(p) + P)
%	\end{align*}
%	If $\dim(P) = \dim(\S_{\gamma_r}(p) + P)$, the claim holds.
%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\S_{\gamma_r}(p) + P) = \|p\|_0$.		
%	One way to do this is to show $\S_{\gamma_r}(p) \subseteq P$.
%	
%	Suppose there was some $v \not\in P$ such that $v \in \S_{\gamma_r}(p)$.
%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
%	However, if $v \in \S_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \S_{\gamma_r}(p)$.
%	Therefore, $\S_{\gamma_r}(p) \subseteq P$, and $\dim(\S_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
\end{proof}

@@

	Now, consider the distribution $p_0$ over $\Y' := \supp(p)$ where each component of $p_0$ is equal to the corresponding entry of $p$.

	If we can show that $L$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$, then we observe the existence of a flat $F^*$ of codimension (in $\reals^{\Y'}$) at most $d$ so that $\dim(F') = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\S_{\gamma'_r}(p_0)) = \dim(\S_{\gamma_r}(p))$, and thus the result holds.

	Now to see that $L$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$, and thus the bound in Equation~\eqref{eq:calibration} is true for all $p \in \Delta_{\Y'}$ as the expected losses are equal for all $y \in \Y'$.
%	Now, if $p \not \in \relint{\simplex}$, we can apply Lemma~\ref{lem:p-boundary-fstar} to observe the existence of an $F^*$ with dimension $\dim(F') - (n - \|p\|_0)$.
%	Moreover, since projecting to $(\{e_y : y \in \supp(p)\})$ does not change the feasible subspace dimension, so we observe the result.
\end{proof}

>>>>

\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, define $\gamma'$ to be $\gamma$ restricted to the simplex $\Delta_{\supp(p)}$.
	Then $\S_{\gamma_r}(p) = \S_{\gamma'_r}(p)$.
\end{lemma}
\begin{proof}
	Consider the ambient space of both $\S_{\gamma_r}(p)$ and $\S_{\gamma'_r}(p)$ to be $\reals^\Y$.
	We trivially have $\S_{\gamma_r}(p) \supseteq \S_{\gamma'_r}(p)$ since the latter is simply a projection down to an affine subspace of the former.

	Now to see $\S_{\gamma_r}(p) \subseteq \S_{\gamma'_r}(p)$, take some $v \not \in \S_{\gamma'_r}(p)$.
	Observe that $\gamma'_r = \gamma_r \cap \Delta_{\supp(p)}$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \Delta_{\supp(p)}$.
	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\Delta_{\supp(p)}$ means one of $q^\pm$ also is not in $\simplex$, and therefore not in $\gamma_r$ and $\gamma_r \subseteq \simplex$.
	Thus $\S_{\gamma_r}(p) = \S_{\gamma'_r}(p)$.
	%commented out 05.26.2020
	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
%	\begin{align*}
%	\dim(\S'_{\gamma_r}(p)) &= \dim(\S_{\gamma_r}(p)) + \dim(P) - \dim(\S_{\gamma_r}(p) + P)
%	\end{align*}
%	If $\dim(P) = \dim(\S_{\gamma_r}(p) + P)$, the claim holds.
%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\S_{\gamma_r}(p) + P) = \|p\|_0$.		
%	One way to do this is to show $\S_{\gamma_r}(p) \subseteq P$.
%	
%	Suppose there was some $v \not\in P$ such that $v \in \S_{\gamma_r}(p)$.
%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
%	However, if $v \in \S_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \S_{\gamma_r}(p)$.
%	Therefore, $\S_{\gamma_r}(p) \subseteq P$, and $\dim(\S_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
\end{proof}

@@

	Now, consider $\Y' := \supp(p)$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y'$.

	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\S_{\gamma'_r}(p)) = \dim(\S_{\gamma_r}(p))$, and thus the result holds.

	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
	\begin{align*}
		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
	\end{align*}
	Therefore, we have $L'$ calibrated with respect to $\ell'$.

	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.

%	Now, if $p \not \in \relint{\simplex}$, we can apply Lemma~\ref{lem:p-boundary-fstar} to observe the existence of an $F^*$ with dimension $\dim(F') - (n - \|p\|_0)$.
%	Moreover, since projecting to $(\{e_y : y \in \supp(p)\})$ does not change the feasible subspace dimension, so we observe the result.
\end{proof}
